---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Covrpage Summary](https://img.shields.io/badge/covrpage-Last_Build_2020_01_26-brightgreen.svg)](http://tinyurl.com/ux5kpl9)
[![R-CMD-check](https://github.com/yonicd/slackcalls/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/yonicd/slackcalls/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/yonicd/slackcalls/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/slackcalls?branch=master)
<!-- badges: end -->

# slackcalls

`slackcalls` is a part of `slackverse`

```{r,echo = FALSE, eval = TRUE}
pkgs <- sprintf('slack%s',c('calls','teams','posts','blocks','threads','reprex'))

badges <- sprintf('%s<br>[![](https://github.com/yonicd/%s/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/yonicd/%s)',pkgs,pkgs,pkgs)

names(badges) <- pkgs

```

||||
|:-:|:-:|:-:|
||`r badges[pkgs[1]]`||
|`r badges[pkgs[5]]`|`r badges[pkgs[2]]`|`r badges[pkgs[3]]`|
|||`r badges[pkgs[4]]`|
|||`r badges[pkgs[6]]`|


`slackcalls` is the backend of `slackverse` it interacts with Slack API methods

  - [Posting](#posting-to-slack)
  - [Querying](#querying-slack)
  - [Storage](#storage)

## Posting to Slack

### Files

Using `files_slack` interact with

  - [files.upload](https://api.slack.com/methods/files.upload)
  - [files.delete](https://api.slack.com/methods/files.delete)
  - [files.info](https://api.slack.com/methods/files.info)
  - [files.list](https://api.slack.com/methods/files.list)

### Chats

Using `chat_slack` interact with

  - [chat.postMessage](https://api.slack.com/methods/chat.postMessage)
  - [chat.delete](https://api.slack.com/methods/chat.delete)
  - [chat.update](https://api.slack.com/methods/chat.update)

## Querying Slack

Using `post_slack` you can query the API to get information such as the following lists. The functions paginate by default. 

### Team

  - [team.info](https://api.slack.com/methods/team.info)
  
### Users

  - [users.list](https://api.slack.com/methods/users.list)
  - [users.info](https://api.slack.com/methods/users.info)

### Conversations

  - [conversations.history](https://api.slack.com/methods/conversations.history)
  - [conversations.list](https://api.slack.com/methods/conversations.list)
  - [conversations.info](https://api.slack.com/methods/conversations.info) 
  - [conversations.members](https://api.slack.com/methods/conversations.members)
  - [conversations.replies](https://api.slack.com/methods/conversations.replies)
  
## Storage

`slackcalls` also saves internally posts that you make during a session in order to use the information for posting to a thread or deleting posts. This mechanism is used in all the slackverse packages.

### Stacks

  - `file_stack`: vector of file IDs that have been sent
  - `post_stack`: list of posts that have been sent, contains information of ID, ts and where relevant thread_ts.

The stacks are updated every time a new post/file is sent or deleted.

### Last Element

using `file_last` and `post_last` you can fetch the head of each stack. 
